\section{Relation to dynamic epistemic logic sequent calculus}
\begin{itemize}
	\item What can we do with my language?
	\item What can we not do with my language?
	\item Introduce Aucher's work in more detail
	\item What can Aucher's work do?
	\item How does it compare to my own work?
	\item Are there any parallels with what we have done?
	\item Is a synthesis of our work possible to achieve a more useful result?
\end{itemize}

So far, we have been particularly interested in constructing event models.
We have shown that we can approximate event models according to what
postconditions are true.
This was through the construction of a particular event model that fulfilled
the postconditions that we aimed to fulfill.\\
\\
This approach is powerful in the sense that we can construct an event model
that, given any Kripke model, will either ensure that a postcondition
is realised or destroy the Kripke model as a result of its execution.
It allows us to guarantee the realisation of a postcondition, without giving
regard to the preceding Kripke model.\\
\\
Another approach to this problem is as follows.
Suppose that we can describe an epistemic situation by a formula $\phi$.
Furthermore, we aim to achieve an epistemic state $\phi''$.
Let $M_s, M''_{s''} \in \kripkeClass$ and $M_s \models \phi$ and $M''_{s''}
\models \phi$, and suppose $M'_{s'} \in \eventClass$ such that $M_s \otimes
M'_{s'} \sim M''_{s''}$.
We are interested in reasoning about all $\phi'$ such that $M'_{s'}
\models \phi'$.\\
\\
Aucher, in \FIXME, discusses a solution to this problem by introducing a
sequent calculus for dynamic epistemic logics.
This sequent calculus allows us to reason about informative updates from
a pre-update epistemic situation to a post-update epistemic situation.

\subsection{Technical Preliminaries}

We reproduce Aucher's sequent calculus

\begin{defn}
Let $\phi, \phi'' \in \lang$ and $\phi' \in \langAct$, we say that
$\phi, \phi'' \models^2 \phi' \iff$ for each $M_s, M''_{s''} \in \kripkeClass$
such that $M_s \models \phi$ and $M''_{s''} \models \phi''$, and every $M'_{s'}
\in \eventClass$ such that $M_s \models pre'(s)$ and $M_s \otimes M'_{s'}
\sim M''_{s''}$ it holds that $M'_{s'} \models \phi'$.
\end{defn}

\begin{itemize}
  \item unsure what else I could put in here...
  \item maybe defining the Sequent Calcuus $SC^2$; see the 2012 paper
  \item what would we be proving though?
\end{itemize}

