\chapter{Project Proposal}

This is the revised project proposal of this dissertation and final year project.

\section{Aim}
%Now state explicitly the hypothesis you aim to
%test. Make references to the items listed in the Reference section
%that back up your arguments for why this is a reasonable
%hypothesis to test, for example the work of Knuth~\cite{knuth}.
%Explain what you expect will be accomplished by undertaking this
%particular project.  Moreover, is it likely to have any other
%applications?
Multi-agent systems are found in many different fields, including
communications, artificial intelligence, game theory and economics.
Modelling these systems as models of Epistemic Logic, we can make formal and
verifiable reasonings about what agents in these systems know, are uncertain
about and are unaware of.
Share trading and auctions are some of the areas where these models are being
applied and further improved.\\
\\
Actions Models are one way to specify an informative update for a multi-agent
system.
They encapsulate the uncertainty between, and potential outcomes of taking an
action.
In a similar way to Epistemic Models, we can make formal and verifiable
reasonings about the updates that agents can employ and what Actions they are
uncertain about.\\
\\
When executed on an Epistemic Model of a multi-agent system, an Action Model
uses the informative update it specifies to change the state of knowledge in the
multi-agent system model.
Recent investigations have yielded methods to synthesise Action Models that can
update an Action Model to ensure that a given condition is true in the updated
Epistemic Model.\\
\\
As a modelling tool for an external user, Action Models are appropriate and
afford a high level of specificity and precision.
However, it is unclear how we can translate an Action Model, which is a formally
specified model applicable to Epistemic Models into a real-world implementation.
How agents involved in a game might use an Action Model or actually realise it
has not been explored.
To come closer to resolving this, we aim to
\begin{itemize}
  \item investigate a formal language that can specify informative updates in
  multi-agent systems
  \item transform Action Models into a series of local informative updates
  between individual agents in a multi-agent system
  \item determining if specific Action Model executions may be made less expensive in
  terms of number of messages, size of messages and complexity of execution
\end{itemize}
%\begin{itemize}
%  \item Discuss action model updates
%  \item Discuss taking an action model that updates many local agents
%  \item Outline how we will derive a series of local updates for agents
%  \item Outline how we this will be implemented
%  \item Outline how we'd like to implement the model
%  \item We want to investigate whether this is a feasibly computed model
%  \item We want to investigate whether an intermediate specification of updates
%    makes action models useful
%\end{itemize}

\section{Background}
%In this section you should give some background to your
%research area. What is the problem you are tackling, and why is it
%worthwhile solving? Who has already done some work in this area,
%and what have they achieved?

Epistemology, in the philosophical sense, concerns the study of knowledge.
Answering questions and issues about the nature, potential and semantics of knowledge have been explored since the times of Ancient Greece.
To answer these questions in an objective fashion, we turn to epistemic logic, the logic of knowledge.
Epistemic logic provides axiomatisations of knowledge that capture its properties.
We can formally reason about an agent's knowledge, its knowledge of its knowledge and (in a system
with multiple agents) other agents' knowledge \cite{hoek2008dynamic}.\\
\\
Agents can be be uncertain about the value for a proposition, resulting in multiple worlds that are consistent with the state of the world.
This ``multiple worlds" agent model is a description of the Kripke model that can be described succinctly by a Kripke model.\footnote{Kripke models can describe more logics than just epistemic logic, depending upon the properties of the relation $R$.}
Kripke models are theoretical constructs that describe for a set of agents $A = \{a_1, a_2, \ldots\}$ and propositions $P = \{p_1, p_2, \ldots \}$
\begin{itemize}
  \item a finite set of states, $S$
  \item a function $R: A \to S \times S$ that yields a relation between states (the accessibility relation for an agent $a$)
  \item a valuation function $V: P \to \mathbb{P}(S)$ that yields for a proposition $p$ the subset of $S$ where $p$ is true
\end{itemize}
Kripke models can be written as a tuple $(S, R, V)$.\\
\\
Epistemic logic only allows us to reason about the state of knowledge, but does not provide us with tools to change or update knowledge.
The study of how the state of information changes is Dynamic Epistemic Logic.
It provides a logical framework of reasoning about how an agent's information and knowledge have changed due to actions.
Recent work in this area includes reasoning about revising beliefs (where an agent's knowledge is invalidated).
Other concepts in this area include public announcements and epistemic actions.
These are informative updates that have specified methods of changing the state of knowledge.
We will focus on a different kind of update: an action model.\\
\\
An epistemic update consists of some action that produces, from model $M = (S, R, V)$ an updated model $M' = (S', R', V')$.
We can encode our action into an action model.
Action models resemble Kripke models in their structure, and consist of a tuple $A = (\bar(S), \bar(R), \bar(pre))$ where
\begin{itemize}
  \item $\bar{S}$ is the set of action model states
  \item $\bar{R}$ is the accessibility relations that for that action; semantically, they represent the uncertainty in taking an action
  \item $\bar{pre}$ is a function that maps a state $s \in \bar{S}$ to a propositional formula that represents the preconditions for that action state to be fulfilled
\end{itemize}
The execution of an action model $A$ to update a Kripke model $M$ to produce $M'$ is a well-understood process.
An update involves taking the Cartesian Product $\bar{S} \times S$ to form the
states of $M'$. \cite{baltag2005programs,baltag1998lpa}
The number of states then dramatically decreases by reduction of the valid states.
This presents a problem in utilising action models to represent an informative update in a computer, due to the expensive nature of an operation like the Cartesian product.\\
\\
There have been attempts to specify formalisations of message passing.
Sietsma suggests a modal logic for reasoning about communication and message passing. \cite{Sietsma:2011:MPD:2000378.2000404}
$\pi$-calculus is another method for program specification and communication in a multi-agent system. \cite{Milner91thepolyadic}
$\pi$-calculus allows us to discuss how programs pass messages between themselves.
%
%\begin {itemize}
%  \item What is epistemic logic?
%  \item What is a Kripke model?
%  \item What is an informative update?
%  \item What is an action model?
%  \item What are the problems with action models?
%\end {itemize}
 
\section{Method}
%In this section you should outline how you intend to go
%about accomplishing the aims you have set in the previous
%section. Try to break your grand aims down into small,
%achievable tasks. Try to estimate how long you will
%spend on each task, and draw up a timetable for each
%sub-task.

We decompose our project outcomes into four separate tasks.
We believe that these separate tasks will together allow us to come closer to
resolving the differences between executing an Action Model on a model of
Epistemic Logic, and executing an Action Model as a series of messages in a game
or message-passing communications system.\\
\\
Firstly, we would like to determine if a generating set exists for action
models, and if not whether there are specific action classes of action models
that we can generate.
Questions that might be resolved include
\begin{itemize}
	\item can we generate all action models?
	\item what is the generating set and what operations would we need to generate
	all action models?
	\item if we cannot generate all action models, what can we not construct and
	would we want to construct it?
\end{itemize}

Secondly, we will investigate how to specify a recursive execution of an action
model.
We will explore how an action model can be realised in a multi-agent system by
first specifying a theoretical way based on pointed action models.
We will attempt to use notions acquired during investigating the generation of
action models to exploit in this recursive execution.
If such a framework cannot be constructed, we will look at what we can execute,
why we cannot execute certain models and decide whether these are updates we
would want to execute.\\
\\
Thirdly, we will implement our recursive framework of action model execution.
This will allow us to perform experimentation and look into the cost of our
action model execution framework.
It would also be desirable to construct our action model generation framework
for experimentation purposes.\\
\\
Finally, using our framework, we will experimentally model how costly our
updates are.
We would like to measure this in terms of time complexity, the time cost to an agent to update
their agent state and the size of the communications made to an agent.
It would be desirable to use these implementation results to reflect theoretical
results about cost of action model execution, and thus allow us to provide some
basis for whether an action model can be executed in a real-world system.
%\begin{enumerate}
%  \item list out different action models, exploring how they update
%    different agents (see Baltag and Moss for a similar exercise)
%  \item specify a model in $\pi$-calculus to update agents
%  \item try and verify model's correctness in replicating action model update
%  \item implement model
%  \item demonstrate its results with the initially explored action models
%  \item test models and find out disadvantages and advantages of models
%\end{enumerate}
%
\section{Software and Hardware Requirements}
%Outline what your specific requirements will be with regard
%to software and hardware, but note that any special requests
%might need to be approved by your supervisor and the Head of
%Department.
At this time, my project does not appear to require any special software or hardware.

\section{Timeline}

\begin{center}
	\begin{tabular}{ | l | p{10cm} |}
		\hline
		Date & Task \\
		\hline
		25 April 2013 & Hand in draft Literature Review and Project Proposal;
    this should allow time to discuss and edit my project proposal as necessary\\
		\hline
		2 May 2013 & Construct a draft introduction that succinctly describes the project purpose and background.\\
		\hline
		16 May 2013 & Edit literature review in line with revised proposal.\\
		\hline
		23 May 2013 & Resubmit literature review \\
		\hline
		7 June 2013 & Draft current ideas about generating sets and operations into
		written work\\
		\hline
		21 June 2013 & Find a generating set and operations for action models \\
		\hline
		28 June 2013 & Re-formalise generation ideas about action models\\
		\hline
		15 July 2013 & Specify a recursive method for executing epistemic updates\\
		\hline
		3 August 2013 & Implement the informative update framework and a framework
		for generating action models\\
		\hline
		10 August 2013 & Draft details about implementation and action model
		execution into written work\\
		\hline
		17 August 2013 & Experiment upon informative updates to measure their cost
		and complexity \\
		\hline
		30 August 2013 & Employ previous experimental results to make claims about
		cost of update execution and formalise them \\
		\hline
		31 August 2013 & Begin writing about specification and the results we have achieved \\
		\hline
		20 September 2013 & Draft thesis due \\
		\hline
	\end{tabular}
\end{center}
