%-----------------------------------------------------------------------------%
%Packages%
\documentclass{cshonours}
\usepackage{amsmath, amsfonts, listings, amssymb, mathtools, amsthm} %Mathematical Expressions package
\usepackage{mathtools}
\usepackage{geometry}
\usepackage{float}
\usepackage{verbatim} %for code
\usepackage[pdftex]{graphics}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{comment}
\usepackage[nottoc]{tocbibind}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algpseudocode}

\usetikzlibrary{arrows,shapes}

%Graphis Extensions
\DeclareGraphicsExtensions{.png, .jpg}
\parindent 0pt

% Predefined things such as commands, etc.

\newtheorem{defn}{Definition}[chapter]
\newtheorem{thm}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corr}{Corollary}[chapter]
\newtheorem{propn}{Proposition}[chapter]
\newtheorem*{remrk}{Remark}
\newcommand{\note}[1]{\textsc{\textbf{#1}}}

\numberwithin{equation}{chapter}

\newcommand{\cover}{\bigtriangledown}
\newcommand{\sqex}[1]{[{#1}]}
\newcommand{\anex}[1]{\langle {#1} \rangle}
\newcommand{\lang}{\ensuremath{L}}
\newcommand{\langRefine}{\ensuremath{\lang_{\forall}}}
\newcommand{\langActEx}{\ensuremath{\lang_{\otimes}}}
\newcommand{\langArbAct}{\ensuremath{\lang_{\otimes\forall}}}
\newcommand{\langProp}{\ensuremath{\lang_0}}

\newcommand{\langKFF}{\ensuremath{K45}}
\newcommand{\lKFFRefine}{\ensuremath{\langKFF_{\forall}}}
\newcommand{\lKFFActEx}{\ensuremath{\langKFF_{\otimes}}}
\newcommand{\lKFFArbAct}{\ensuremath{\langKFF_{\otimes\forall}}}
\newcommand{\lKFFProp}{\ensuremath{\langKFF_0}}

\newcommand{\AXK}{\ensuremath{\bf K}}
\newcommand{\AXKFF}{\ensuremath{\bf K45}}
\newcommand{\AXAML}{\ensuremath{\bf AML_{\AXK}}}
\newcommand{\AXRML}{\ensuremath{\bf RML_{\AXK}}}
\newcommand{\AXAAML}{\ensuremath{\bf AAML_{\AXK}}}

\newcommand{\axP}{\ensuremath{\bf P}}
\newcommand{\axK}{\ensuremath{\bf K}}
\newcommand{\axFo}{\ensuremath{\bf 4}}
\newcommand{\axFi}{\ensuremath{\bf 5}}
\newcommand{\axMP}{\ensuremath{\bf MP}}
\newcommand{\axNecK}{\ensuremath{\bf NecK}}
\newcommand{\axAN}{\ensuremath{\bf AN}}
\newcommand{\axAP}{\ensuremath{\bf AP}}
\newcommand{\axAC}{\ensuremath{\bf AC}}
\newcommand{\axAK}{\ensuremath{\bf AK}}
\newcommand{\axAU}{\ensuremath{\bf AU}}
\newcommand{\axNecA}{\ensuremath{\bf NecA}}
\newcommand{\axR}{\ensuremath{\bf R}}
\newcommand{\axRP}{\ensuremath{\bf RP}}
\newcommand{\axRK}{\ensuremath{\bf RK}}
\newcommand{\axRComm}{\ensuremath{\bf RComm}}
\newcommand{\axRDist}{\ensuremath{\bf RDist}}
\newcommand{\axNecR}{\ensuremath{\bf NecR}}

\newcommand{\krMo}{M}
\newcommand{\aMod}[1]{
  \ensuremath {\mathrm{\mathsf{#1}}}
}
\newcommand{\evMo}{\aMod{N}}
\newcommand{\evM}{\evMo}
\newcommand{\evMM}{\aMod{M}}
\newcommand{\evS}{\aMod{S}}
\newcommand{\evR}{\aMod{R}}
\newcommand{\evpr}{\aMod{pre}}
\newcommand{\evpre}{\evpr}
\newcommand{\evT}{\aMod{T}}
\newcommand{\evU}{\aMod{U}}
\newcommand{\evr}{\aMod{r}}
\newcommand{\evs}{\aMod{s}}
\newcommand{\evt}{\aMod{t}}
\newcommand{\evu}{\aMod{u}}
\newcommand{\evv}{\aMod{v}}
\newcommand{\evp}{\aMod{p}}
\newcommand{\evq}{\aMod{q}}

\newcommand{\kripkeClass}{\mathcal{K}}
\newcommand{\eventClass}{\mathcal{AM}}
\newcommand{\EM}{\ensuremath{\eventClass}}
\newcommand{\insaneClass}{\eventClass_{IN}}
\newcommand{\publicAnnClass}{\eventClass_{PA}}
\newcommand{\treeClass}{\eventClass_{TR}}
\newcommand{\forestClass}{\eventClass_{FOR}}

\newcommand{\mDep}{ {\bf MD}}

\newcommand{\FIXME}{{\bf FIXME}}
% Drawings of frames

\tikzstyle{vertex}=[circle,draw=black!100,thick,fill=black!25,minimum size=20pt,inner sep=0pt]
\tikzstyle{selected vertex} = [vertex, fill=red!24]
\tikzstyle{edge} = [draw,thick,->]
\tikzstyle{weight} = [font=\small]

%-----------------------------------------------------------------------------%
%Document%

\title{Languages for epistemic action model synthesis in multi-agent systems}
\author{Edwin Richard Yucheng Tay \\
University of Western Australia \\
email: taye03@student.uwa.edu.au }

\date{\today}

\keywords{Dynamic epistemic logic, action model synthesis, epistemic logic}
\categories{F.4.1, I.2.4}

\begin{document}

\maketitle

\begin{abstract}

Action models are theoretical updates whose after-effects we can reason about
and prove.
They are powerful specifications of updates of knowledge and belief in
multi-agent systems.
These formal properties of structure and provability are much-desired in
fields where formal reasonings and correctness are central.
Safety critical systems are one such area where updates that are provably
correct are extremely helpful.
Other areas include game theory, finances, model checking and formal methods in
software engineering, where updates and dynamics are finding increasing applicability.\\
\\
Very little has been done in the way of composing action models --- that is, combining smaller,
``atomic" action models into a larger one through the means of meaningful operations.
This work contributes to this area, by specifying languages for action model composition.
Within this paper, two different composition frameworks for two logics will be shown, one in
the $\lang$ and one in $\langKFF$.
We prove that these action models are able to realise the same after effects of
any other action model in these logics.
We then discuss the open questions with regards to action model construction
that have been raised by this paper.

\end{abstract}

\begin{acknowledgements}
I would like to acknowledge Tim French and James Hales for their valued assistance during this final
year engineering project.\\
Tim has reviewed many iterations of this dissertation, in both its incomplete forms and as a fully
fledged document, and provided insights and guidance on how to improve my writing and approach to
the dissertation.
Each iteration has been returned to me with helpful feedback and notes on how to improve the
dissertation to a level that we have been satisfied with, and the time invested in meeting with me,
whether it was scheduled or not, has been much appreciated.\\
James has been kind enough to give valuable feedback regarding my work and to suggest some useful and
constructive structural changes that improve the logical flow of the work.
I appreciate all the help he has given to a struggling final year engineering student in both
finding quality sources of academic literature, as well as understanding some of the subtleties of modal logic.
\end{acknowledgements}

\pagebreak

\tableofcontents

\listoffigures

\include{./introduction}
\include{./survey}
\include{./preliminary}
\include{./multiagent}
\include{./k45}
\include{./conclusion}
% appendices

\appendix

\include{./axioms}
\include{./proofs}
\include{./proposal}

\bibliographystyle{acm}
\bibliography{thesis}

\end{document}
